---
title: "Aphasia Demographics"
author: "Jennifer Lee (hlee1), Dai Chen (daic)"
date: "February 22, 2016"
output: pdf_document
---

```{r, cache=TRUE}
dem2 = read.csv("demographics-2 and subtest scores.csv", header=TRUE)
dem2 = dem2[1:51,1:5]

dem2wab = read.csv("demographics-2 WAB.csv", header=TRUE, skip=1)
dem2wab = dem2wab[,-1]

dem2clqt = read.csv("demographics-2 CLQT.csv", header=TRUE, skip=1)
dem2clqt = dem2clqt[,-1]

dem2bnt = read.csv("demographics-2 BNT.csv", header=TRUE, skip=1)
dem2bnt = dem2bnt[,-1]

dem2papt = read.csv("demographics-2 PAPT.csv", header=TRUE, skip=1)
dem2papt = dem2papt[,-1]
```

```{r, fig.height=12, fig.width=8}
library(pander)
dem = cbind(dem2, dem2wab, dem2clqt, dem2bnt, dem2papt)
names(dem) = tolower(names(dem))


controls = c(12,19, 20, 26, 27, 28, 39, 47, 48)
dem$control = 0
dem[controls, "control"]=1
dem$control = factor(dem$control, levels=c(0,1), labels=c("Treat", "Control"))

temp = dem$education
temp = droplevels(temp)
temp[temp=="unknown"]=NA
as.numeric(as.character(temp))

```

This will not run yet, the code needs to be cleaned

par(mfrow=c(3,2))
boxplot(dem$age~dem$control, main="Age distribution", xlab="Patient type",
        ylab="Age")
boxplot(as.numeric(dem$education)~dem$control, main="Education distribution", xlab="Patient type",
        ylab="Age")

boxplot(dem$language.quotient~dem$control, main="Pre WAB LQ score distribution", 
        xlab="Patient type", ylab="WAB LQ score")
boxplot(dem$language.quotient.1~dem$control, main="Post WAB LQ score distribution", 
        xlab="Patient type", ylab="WAB LQ score")

boxplot(dem$cortical.quotient~dem$control, main="Pre WAB CQ score distribution", 
        xlab="Patient type", ylab="WAB CQ score")
boxplot(dem$cortical.quotient.1~dem$control, main="Post WAB CQ score distribution", 
        xlab="Patient type", ylab="WAB CQ score")

boxplot(dem$aphasia.quotient~dem$control, main="Pre WAB AQ score distribution", 
        xlab="Patient type", ylab="WAB AQ score")
boxplot(dem$aphasia.quotient.1~dem$control, main="Post WAB AQ score distribution", 
        xlab="Patient type", ylab="WAB AQ score")

boxplot(as.numeric(dem$clqt.attention)~dem$control, main="Pre CLQT attention distribution", 
        xlab="Patient type", ylab="CLQT attention score")
boxplot(as.numeric(dem$clqt.attention.1)~dem$control, main="Post CLQT attention distribution", 
        xlab="Patient type", ylab="CLQT attention score")

boxplot(as.numeric(dem$clqt.memory)~dem$control, main="Pre CLQT memory distribution", 
        xlab="Patient type", ylab="CLQT memory score")
boxplot(as.numeric(dem$clqt.memory.1)~dem$control, main="Post CLQT memory distribution", 
        xlab="Patient type", ylab="CLQT memory score")

pander(table(dem$aphasia.type, dem$control))
pander(table(dem$aphasia.type.1, dem$control))
```
